Summary Tables

### 2019-05-08 summary_tables_outcomes.Rmd
new results tables

@@

death_totals_rounded <- lapply(death_totals, function(x)round(x,round_to))

death_totals_rounded <- lapply(death_totals_rounded,function(x)rbind(x,Total=colSums(x)))

for(city in cities) {
  print(kable(death_totals_rounded[[city]], caption = paste("Change in deaths total in ", city)))
  cat("\n")
}
```

@@

death_rates_rounded <- lapply(death_rates, function(x)round(x,round_to))

death_rates_rounded <- lapply(death_rates_rounded,function(x)rbind(x,Total=colSums(x)))

for(city in cities) {
  print(kable(death_rates_rounded[[city]], caption = paste("Change in deaths per 100,000 in ", city)))
  cat("\n")
}
```

@@

```{r scen_prop = "asis"}
yll_totals <- lapply(io,function(x){
  temp <- sapply(1:5,function(y){
    xx <- x$outcomes$hb$ylls
    xxx <- rowSums(xx[,seq(2+y,ncol(xx),by=5)])
    sapply(sort(unique(xx$age_cat)),function(z)
      sum(xxx[xx$age_cat==z]))
  })
  colnames(temp) <- scen_names
  temp
  })
yll_totals_rounded <- lapply(yll_totals,function(x)rbind(x,Total=colSums(x)))
yll_totals_rounded <- lapply(yll_totals_rounded, function(x)round(x,round_to))

for(city in cities) {
  print(kable(yll_totals_rounded[[city]], caption = paste("Change in YLL total in ", city)))
  cat("\n")
}
```

@@

```{r scen_prop = "asis"}
yll_rates <- lapply(cities,function(x) yll_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000)
names(yll_rates) <- cities
yll_rates_rounded <- lapply(yll_rates,function(x)rbind(x,Total=colSums(x)))
yll_rates_rounded <- lapply(yll_rates_rounded, function(x)round(x,round_to))

for(city in cities) {
  print(kable(yll_rates_rounded[[city]], caption = paste("Change in YLLs per 100,000 in ", city)))
  cat("\n")
}
```

@@

yll_rates <- lapply(cities,function(x) 
  yll_totals[[x]][match(apply(io[[x]]$demographic[,c('sex','age')],1,function(z)paste0(z[2],'_',z[1])),rownames(yll_totals[[x]])),]/
    t(repmat(io[[x]]$demographic$population,5,1))*100000)
names(yll_rates) <- cities
yll_rates_rounded <- lapply(yll_rates,function(x)rbind(x,Total=colSums(x)))
yll_rates_rounded <- lapply(yll_rates_rounded, function(x)round(x,round_to))

for(city in cities) {
  print(kable(yll_rates_rounded[[city]], caption = paste("Change in YLLs per 100,000 in ", city)))
  cat("\n")
}
```

@@

```{r}
injury_totals <- lapply(io,function(x){
  xx <- x$outcomes$hb$deaths
  xxx <- sapply(1:5,function(y)sapply(sort(unique(xx$age_cat)),function(z)sum(xx[xx$age_cat==z,injury_col-1+y])))
  colnames(xxx) <- scen_names
  xxx
  })
injury_totals_rounded <- lapply(injury_totals,function(x)rbind(x,Total=colSums(x)))
injury_totals_rounded <- lapply(injury_totals_rounded, function(x)round(x,round_to))

for(city in cities) {
  print(kable(injury_totals_rounded[[city]], caption = paste("Change in deaths due to injury in ", city)))
  cat("\n")
}

pa_totals <- lapply(io,function(x){
  xx <- x$outcomes$pathway_hb$deaths
  xxx <- sapply(1:5,function(y){
    xxx <- rowSums(xx[,pa_cols[seq(y,length(pa_cols),by=5)]])
    sapply(sort(unique(xx$age_cat)),function(z)sum(xxx[xx$age_cat==z]))
  })
  colnames(xxx) <- scen_names
  xxx
  })
pa_totals_rounded <- lapply(pa_totals,function(x)rbind(x,Total=colSums(x)))
pa_totals_rounded <- lapply(pa_totals_rounded, function(x)round(x,round_to))

for(city in cities) {
  print(kable(pa_totals_rounded[[city]], caption = paste("Change in deaths due to PA in ", city)))
  cat("\n")
}

ap_totals <- lapply(io,function(x){
  xx <- x$outcomes$pathway_hb$deaths
  xxx <- sapply(1:5,function(y){
    xxx <- rowSums(xx[,ap_cols[seq(y,length(ap_cols),by=5)]])
    sapply(sort(unique(xx$age_cat)),function(z)sum(xxx[xx$age_cat==z]))
  })
  colnames(xxx) <- scen_names
  xxx
  })
ap_totals_rounded <- lapply(ap_totals,function(x)rbind(x,Total=colSums(x)))
ap_totals_rounded <- lapply(ap_totals_rounded, function(x)round(x,round_to))

for(city in cities) {
  print(kable(ap_totals_rounded[[city]], caption = paste("Change in deaths due to AP in ", city)))
  cat("\n")
}
```

@@

```{r scen_prop = "asis"}
injury_rates <- lapply(cities,function(x) injury_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000)
names(injury_rates) <- cities
injury_rates_rounded <- lapply(injury_rates,function(x)rbind(x,Total=colSums(x)))
injury_rates_rounded <- lapply(injury_rates_rounded, function(x)round(x,round_to))

for(city in cities) {
  print(kable(injury_rates_rounded[[city]], caption = paste("Change in deaths due to injury per 100,000 in ", city)))
  cat("\n")
}
```

@@

```{r}
injury_totals <- lapply(io,function(x){
  xx <- x$outcomes$hb$ylls
  xxx <- sapply(1:5,function(y)sapply(sort(unique(xx$age_cat)),function(z)sum(xx[xx$age_cat==z,injury_col-1+y])))
  colnames(xxx) <- scen_names
  xxx
  })
injury_totals_rounded <- lapply(injury_totals,function(x)rbind(x,Total=colSums(x)))
injury_totals_rounded <- lapply(injury_totals_rounded, function(x)round(x,round_to))

for(city in cities) {
  print(kable(injury_totals_rounded[[city]], caption = paste("Change in YLLs due to injury in ", city)))
  cat("\n")
}
```

@@

```{r scen_prop = "asis"}
injury_rates <- lapply(cities,function(x) injury_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000)
names(injury_rates) <- cities
injury_rates_rounded <- lapply(injury_rates,function(x)rbind(x,Total=colSums(x)))
injury_rates_rounded <- lapply(injury_rates_rounded, function(x)round(x,round_to))

for(city in cities) {
  print(kable(injury_rates_rounded[[city]], caption = paste("Change in YLLs due to injury per 100,000 in ", city)))
  cat("\n")
}
```

@@

disease_totals <- lapply(io,function(x){
  xx <- x$outcomes$hb$deaths
  xxx <- sapply(1:5,function(y){
    colSums(xx[,seq(y+2,ncol(xx),by=5)])
  })
  colnames(xxx) <- scen_names
  rownames(xxx) <- sapply(rownames(xxx),function(y)gsub('scen1_','',y))
  xxx
  })
disease_totals_rounded <- lapply(disease_totals,function(x)rbind(x,Total=colSums(x)))
disease_totals_rounded <- lapply(disease_totals_rounded, function(x)round(x,round_to))

for(city in cities) {
  print(kable(disease_totals_rounded[[city]], caption = paste("Change in deaths due to disease in ", city)))
  cat("\n")
}

@@

```{r scen_prop = "asis"}
disease_rates <- lapply(cities,function(x) disease_totals[[x]]/sum(pop_by_age[[x]])*100000)
names(disease_rates) <- cities
disease_rates_rounded <- lapply(disease_rates,function(x)rbind(x,Total=colSums(x)))
disease_rates_rounded <- lapply(disease_rates_rounded, function(x)round(x,round_to))

for(city in cities) {
  print(kable(disease_rates_rounded[[city]], caption = paste("Change in deaths due to disease per 100,000 in ", city)))
  cat("\n")
}
```

@@

disease_totals <- lapply(io,function(x){
  xx <- x$outcomes$hb$ylls
  xxx <- sapply(1:5,function(y){
    colSums(xx[,seq(y+2,ncol(xx),by=5)])
  })
  colnames(xxx) <- scen_names
  rownames(xxx) <- sapply(rownames(xxx),function(y)gsub('scen1_','',y))
  xxx
  })
disease_totals_rounded <- lapply(disease_totals,function(x)rbind(x,Total=colSums(x)))
disease_totals_rounded <- lapply(disease_totals_rounded, function(x)round(x,round_to))

for(city in cities) {
  print(kable(disease_totals_rounded[[city]], caption = paste("Change in YLL due to disease in ", city)))
  cat("\n")
}

@@

```{r scen_prop = "asis"}
disease_rates <- lapply(cities,function(x) disease_totals[[x]]/sum(pop_by_age[[x]])*100000)
names(disease_rates) <- cities
disease_rates_rounded <- lapply(disease_rates,function(x)rbind(x,Total=colSums(x)))
disease_rates_rounded <- lapply(disease_rates_rounded, function(x)round(x,round_to))

for(city in cities) {
  print(kable(disease_rates_rounded[[city]], caption = paste("Change in YLL due to disease per 100,000 in ", city)))
  cat("\n")
}
```

>>>>

sum_and_round_and_print <- function(data,text=''){
  data <- lapply(data, function(x)round(x,round_to))
  data <- lapply(data,function(x)rbind(x,Total=colSums(x)))
  for(city in cities) {
    print(kable(data[[city]], caption = paste(text, city)))
    cat("\n")
  }
}

@@

sum_and_round_and_print(death_totals,"Change in deaths total in ")
```

@@

sum_and_round_and_print(death_rates,"Change in deaths per 100,000 in ")
```

@@

```{r scen_prop = "asis"}
yll_totals <- lapply(io,function(x){
  temp <- sapply(1:5,function(y){
    xx <- x$outcomes$hb$ylls
    xxx <- rowSums(xx[,seq(2+y,ncol(xx),by=5)])
    sapply(sort(unique(xx$age_cat)),function(z)
      sum(xxx[xx$age_cat==z]))
  })
  colnames(temp) <- scen_names
  temp
  })
sum_and_round_and_print(yll_totals,"Change in YLL total in ")
```

@@

```{r scen_prop = "asis"}
yll_rates <- lapply(cities,function(x) yll_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000)
names(yll_rates) <- cities
sum_and_round_and_print(yll_rates,"Change in YLLs per 100,000 in ")
```

@@

yll_rates <- lapply(cities,function(x) 
  yll_totals[[x]][match(apply(io[[x]]$demographic[,c('sex','age')],1,function(z)paste0(z[2],'_',z[1])),rownames(yll_totals[[x]])),]/
    t(repmat(io[[x]]$demographic$population,5,1))*100000)
names(yll_rates) <- cities
sum_and_round_and_print(yll_rates,"Change in YLLs per 100,000 in ")
```

@@

```{r}
injury_totals <- lapply(io,function(x){
  xx <- x$outcomes$hb$deaths
  xxx <- sapply(1:5,function(y)sapply(sort(unique(xx$age_cat)),function(z)sum(xx[xx$age_cat==z,injury_col-1+y])))
  colnames(xxx) <- scen_names
  xxx
  })
sum_and_round_and_print(injury_totals,"Change in deaths due to injury in ")

pa_totals <- lapply(io,function(x){
  xx <- x$outcomes$pathway_hb$deaths
  xxx <- sapply(1:5,function(y){
    xxx <- rowSums(xx[,pa_cols[seq(y,length(pa_cols),by=5)]])
    sapply(sort(unique(xx$age_cat)),function(z)sum(xxx[xx$age_cat==z]))
  })
  colnames(xxx) <- scen_names
  xxx
  })
sum_and_round_and_print(pa_totals,"Change in deaths due to PA in ")

ap_totals <- lapply(io,function(x){
  xx <- x$outcomes$pathway_hb$deaths
  xxx <- sapply(1:5,function(y){
    xxx <- rowSums(xx[,ap_cols[seq(y,length(ap_cols),by=5)]])
    sapply(sort(unique(xx$age_cat)),function(z)sum(xxx[xx$age_cat==z]))
  })
  colnames(xxx) <- scen_names
  xxx
  })
sum_and_round_and_print(ap_totals,"Change in deaths due to AP in ")
```

@@

```{r scen_prop = "asis"}
injury_rates <- lapply(cities,function(x) injury_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000)
names(injury_rates) <- cities
sum_and_round_and_print(injury_rates,"Change in deaths due to injury per 100,000 in ")

pa_rates <- lapply(cities,function(x) pa_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000)
names(pa_rates) <- cities
sum_and_round_and_print(pa_rates,"Change in deaths due to PA per 100,000 in ")

ap_rates <- lapply(cities,function(x) ap_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000)
names(ap_rates) <- cities
sum_and_round_and_print(ap_rates,"Change in deaths due to AP per 100,000 in ")
```

@@

```{r}
injury_totals <- lapply(io,function(x){
  xx <- x$outcomes$hb$ylls
  xxx <- sapply(1:5,function(y)sapply(sort(unique(xx$age_cat)),function(z)sum(xx[xx$age_cat==z,injury_col-1+y])))
  colnames(xxx) <- scen_names
  xxx
  })
sum_and_round_and_print(injury_totals,"Change in YLLs due to injury in ")

pa_totals <- lapply(io,function(x){
  xx <- x$outcomes$pathway_hb$ylls
  xxx <- sapply(1:5,function(y){
    xxx <- rowSums(xx[,pa_cols[seq(y,length(pa_cols),by=5)]])
    sapply(sort(unique(xx$age_cat)),function(z)sum(xxx[xx$age_cat==z]))
  })
  colnames(xxx) <- scen_names
  xxx
  })
sum_and_round_and_print(pa_totals,"Change in YLLs due to PA in ")

ap_totals <- lapply(io,function(x){
  xx <- x$outcomes$pathway_hb$ylls
  xxx <- sapply(1:5,function(y){
    xxx <- rowSums(xx[,ap_cols[seq(y,length(ap_cols),by=5)]])
    sapply(sort(unique(xx$age_cat)),function(z)sum(xxx[xx$age_cat==z]))
  })
  colnames(xxx) <- scen_names
  xxx
  })
sum_and_round_and_print(ap_totals,"Change in YLLs due to AP in ")
```

@@

```{r scen_prop = "asis"}
injury_rates <- lapply(cities,function(x) injury_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000)
names(injury_rates) <- cities
sum_and_round_and_print(injury_rates,"Change in YLLs due to injury per 100,000 in ")

pa_rates <- lapply(cities,function(x) pa_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000)
names(pa_rates) <- cities
sum_and_round_and_print(pa_rates,"Change in YLLs due to PA per 100,000 in ")

ap_rates <- lapply(cities,function(x) ap_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000)
names(ap_rates) <- cities
sum_and_round_and_print(ap_rates,"Change in YLLs due to AP per 100,000 in ")
```

@@

disease_totals <- lapply(io,function(x){
  xx <- x$outcomes$hb$deaths
  xxx <- sapply(1:5,function(y){
    colSums(xx[,seq(y+2,ncol(xx),by=5)])
  })
  colnames(xxx) <- scen_names
  rownames(xxx) <- sapply(rownames(xxx),function(y)gsub('scen1_','',y))
  xxx
  })
sum_and_round_and_print(disease_totals,"Change in deaths due to disease in ")

@@

```{r scen_prop = "asis"}
disease_rates <- lapply(cities,function(x) disease_totals[[x]]/sum(pop_by_age[[x]])*100000)
names(disease_rates) <- cities
sum_and_round_and_print(disease_rates,"Change in deaths due to disease per 100,000 in ")
```

@@

disease_totals <- lapply(io,function(x){
  xx <- x$outcomes$hb$ylls
  xxx <- sapply(1:5,function(y){
    colSums(xx[,seq(y+2,ncol(xx),by=5)])
  })
  colnames(xxx) <- scen_names
  rownames(xxx) <- sapply(rownames(xxx),function(y)gsub('scen1_','',y))
  xxx
  })
sum_and_round_and_print(disease_totals,"Change in YLL due to disease in ")

@@

```{r scen_prop = "asis"}
disease_rates <- lapply(cities,function(x) disease_totals[[x]]/sum(pop_by_age[[x]])*100000)
names(disease_rates) <- cities
sum_and_round_and_print(disease_rates,"Change in YLL due to disease per 100,000 in ")
```
